---
title: "Stacking 2014-2019"
author: "Gagarin Zhao"
date: "8/13/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(openxlsx)
```


Export years 2016-2018 joined as XLSX. Following years can be added as time goes on.
Table 6a (services) will be compiled separately.

```{r Binding all years to date, table 5 + 5a}

uds2016to2018info.t5.T5A = bind_rows(uds2016info.t5.T5A, uds2017info.t5.T5A, uds2018info.t5.T5A)

write.xlsx(uds2016to2018info.t5.T5A, "C:\\Users\\GagarinZhao\\Documents\\Work\\UDS\\Data Wrangling\\uds2016to2018info_T5_T5A.xlsx", overwrite = TRUE)
```


Pulling 2019 table 5 data, only variables that exist in previous years:


```{r pulling 2019}
uds2019info.t5_rel = uds2019info.t5 %>% 
  select(BHCMISID,
         ReportingYear,
         HealthCenterName,
         T5_L8_Ca, #table 5
         T5_L8_Cb,
         T5_L8_Cb2,
         T5_L11_Ca,
         T5_L11_Cb,
         T5_L11_Cb2,
         T5_L10a_Ca,
         T5_L10a_Cb,
         T5_L10a_Cb2,
         T5_L15_Ca,
         T5_L15_Cb,
         T5_L15_Cb2,
         T5_L15_Cc,
         T5_L19_Ca,
         T5_L19_Cb,
         T5_L19_Cb2,
         T5_L19_Cc,
         T5_L20_Ca,
         T5_L20_Cb,
         T5_L20_Cb2,
         T5_L20_Cc,
         T5_L21_Ca,
         T5_L21_Cb,
         T5_L21_Cb2,
         T5_L21_Cc,
         T5_L22_Ca,
         T5_L22_Cb,
         T5_L22_Cb2,
         T5_L22_Cc,
         T5_L22d_Ca,
         T5_L22d_Cb,
         T5_L22d_Cb2,
         T5_L22d_Cc,
         T5_L29_Ca,
         T5_L29_Cb,
         T5_L29_Cb2,
         T5_L29_Cc,
         T5_L34_Ca,
         T5_L34_Cb,
         T5_L34_Cb2)
```

Years 2014 and 2015 columns don't quite match following years. I pull specific columns and do a second bind:

```{r pulling 2014 and 2015}
uds2014info.t5_rel = uds2014info.t5.T5A %>% 
  select(BHCMISID,
         ReportingYear,
         HealthCenterName,
         T5_L8_Ca, #table 5
         T5_L8_Cb,
         T5_L11_Ca,
         T5_L11_Cb,
         T5_L10a_Ca,
         T5_L10a_Cb,
         T5_L15_Ca,
         T5_L15_Cb,
         T5_L15_Cc,
         T5_L19_Ca,
         T5_L19_Cb,
         T5_L19_Cc,
         T5_L20_Ca,
         T5_L20_Cb,
         T5_L20_Cc,
         T5_L21_Ca,
         T5_L21_Cb,
         T5_L21_Cc,
         T5_L22_Ca,
         T5_L22_Cb,
         T5_L22_Cc,
         T5_L22d_Ca,
         T5_L22d_Cb,
         T5_L22d_Cc,
         T5_L29_Ca,
         T5_L29_Cb,
         T5_L29_Cc,
         T5_L34_Ca,
         T5_L34_Cb)

uds2014info.T5A_rel = uds2014info.t5.T5A %>% 
  select(#table 5a
    BHCMISID,
         ReportingYear,
         HealthCenterName,
         T5A_L1_Ca,
         T5A_L1_Cb,
         T5A_L2_Ca,
         T5A_L2_Cb,
         T5A_L3_Ca,
         T5A_L3_Cb,
         T5A_L4_Ca,
         T5A_L4_Cb,
         T5A_L5_Ca,
         T5A_L5_Cb,
         T5A_L7_Ca,
         T5A_L7_Cb,
         T5A_L9a_Ca,
         T5A_L9a_Cb,
         T5A_L9b_Ca,
         T5A_L9b_Cb,
         T5A_L10_Ca,
         T5A_L10_Cb,
         T5A_L11_Ca,
         T5A_L11_Cb,
         T5A_L16_Ca,
         T5A_L16_Cb,
         T5A_L17_Ca,
         T5A_L17_Cb,
        # T5A_L17a_Ca, does not exist this year
        # T5A_L17a_Cb,
         T5A_L20a_Ca,
         T5A_L20a_Cb,
         T5A_L20a1_Ca,
         T5A_L20a1_Cb,
         T5A_L20a2_Ca,
         T5A_L20a2_Cb,
         T5A_L20b_Ca,
         T5A_L20b_Cb,
         T5A_L22a_Ca,
         T5A_L22a_Cb,
         T5A_L22b_Ca,
         T5A_L22b_Cb,
         T5A_L30a1_Ca,
         T5A_L30a1_Cb,
         T5A_L30a2_Ca,
         T5A_L30a2_Cb,
         T5A_L30a3_Ca,
         T5A_L30a3_Cb,
         T5A_L30a4_Ca,
         T5A_L30a4_Cb)

uds2015info.t5_rel = uds2015info.t5.T5A %>% 
  select(BHCMISID,
         ReportingYear,
         HealthCenterName,
         T5_L8_Ca, #table 5
         T5_L8_Cb,
         T5_L11_Ca,
         T5_L11_Cb,
         T5_L10a_Ca,
         T5_L10a_Cb,
         T5_L15_Ca,
         T5_L15_Cb,
         T5_L15_Cc,
         T5_L19_Ca,
         T5_L19_Cb,
         T5_L19_Cc,
         T5_L20_Ca,
         T5_L20_Cb,
         T5_L20_Cc,
         T5_L21_Ca,
         T5_L21_Cb,
         T5_L21_Cc,
         T5_L22_Ca,
         T5_L22_Cb,
         T5_L22_Cc,
         T5_L22d_Ca,
         T5_L22d_Cb,
         T5_L22d_Cc,
         T5_L29_Ca,
         T5_L29_Cb,
         T5_L29_Cc,
         T5_L34_Ca,
         T5_L34_Cb)

uds2015info.T5A_rel = uds2015info.t5.T5A %>% 
  select(#table 5a
         BHCMISID,
         ReportingYear,
         HealthCenterName,
         T5A_L1_Ca,
         T5A_L1_Cb,
         T5A_L2_Ca,
         T5A_L2_Cb,
         T5A_L3_Ca,
         T5A_L3_Cb,
         T5A_L4_Ca,
         T5A_L4_Cb,
         T5A_L5_Ca,
         T5A_L5_Cb,
         T5A_L7_Ca,
         T5A_L7_Cb,
         T5A_L9a_Ca,
         T5A_L9a_Cb,
         T5A_L9b_Ca,
         T5A_L9b_Cb,
         T5A_L10_Ca,
         T5A_L10_Cb,
         T5A_L11_Ca,
         T5A_L11_Cb,
         T5A_L16_Ca,
         T5A_L16_Cb,
         T5A_L17_Ca,
         T5A_L17_Cb,
         # T5A_L17a_Ca,
         # T5A_L17a_Cb, does exist this year
         T5A_L20a_Ca,
         T5A_L20a_Cb,
         T5A_L20a1_Ca,
         T5A_L20a1_Cb,
         T5A_L20a2_Ca,
         T5A_L20a2_Cb,
         T5A_L20b_Ca,
         T5A_L20b_Cb,
         T5A_L22a_Ca,
         T5A_L22a_Cb,
         T5A_L22b_Ca,
         T5A_L22b_Cb,
         T5A_L30a1_Ca,
         T5A_L30a1_Cb,
         T5A_L30a2_Ca,
         T5A_L30a2_Cb,
         T5A_L30a3_Ca,
         T5A_L30a3_Cb,
         T5A_L30a4_Ca,
         T5A_L30a4_Cb
         )

uds2014to2019info.t5.T5A = bind_rows(uds2016to2018info.t5.T5A, uds2014info.t5.T5A_rel, uds2015info.t5.T5A_rel)
```



Calculating productivity + renaming for easier usage in PowerBI. Other variables can be quickly added here.

```{r table 5}
T5_rel_numbers = uds2016to2018info.t5.T5A %>% 
  select(BHCMISID,
         ReportingYear,
         HealthCenterName,
         T5_L8_Ca, #table 5
         T5_L8_Cb,
         T5_L11_Ca,
         T5_L11_Cb,
         T5_L10a_Ca,
         T5_L10a_Cb,
         T5_L15_Ca,
         T5_L15_Cb,
         T5_L15_Cc,
         T5_L19_Ca,
         T5_L19_Cb,
         T5_L19_Cc,
         T5_L20_Ca,
         T5_L20_Cb,
         T5_L20_Cc,
         T5_L21_Ca,
         T5_L21_Cb,
         T5_L21_Cc,
         T5_L22_Ca,
         T5_L22_Cb,
         T5_L22_Cc,
         T5_L22d_Ca,
         T5_L22d_Cb,
         T5_L22d_Cc,
         T5_L29_Ca,
         T5_L29_Cb,
         T5_L29_Cc,
         T5_L34_Ca,
         T5_L34_Cb) %>% 
  bind_rows(uds2014info.t5_rel, uds2015info.t5_rel, uds2019info.t5_rel) %>% #TACK ON 2014, 2015, 2019
  mutate(total_phys_vis_by_fte = T5_L8_Cb/T5_L8_Ca, #calculations
         nurses_vis_by_fte = T5_L11_Cb/T5_L11_Ca,
         total_NP_PA_CNM_vis_by_fte = T5_L10a_Cb/T5_L10a_Ca,
         total_med_vis_by_fte = T5_L15_Cb/T5_L15_Ca,
         total_med_pat_by_fte = T5_L15_Cc/T5_L15_Ca,
         total_dental_vis_by_fte = T5_L19_Cb/T5_L19_Ca,
         total_dental_pat_by_fte = T5_L19_Cc/T5_L19_Ca,
         total_mental_vis_by_fte = T5_L20_Cb/T5_L20_Ca,
         total_mental_pat_by_fte = T5_L20_Cc/T5_L20_Ca,
         total_SUD_vis_by_fte = T5_L21_Cb/T5_L21_Ca,
         total_SUD_pat_by_fte = T5_L21_Cc/T5_L21_Ca,         
         total_otherprof_vis_by_fte = T5_L22_Cb/T5_L22_Ca,
         total_otherprof_pat_by_fte = T5_L22_Cc/T5_L22_Ca,   
         total_vision_vis_by_fte = T5_L22d_Cb/T5_L22d_Ca,
         total_vision_pat_by_fte = T5_L22d_Cc/T5_L22d_Ca,
         total_enabling_vis_by_fte = T5_L29_Cb/T5_L29_Ca,
         total_enabling_pat_by_fte = T5_L29_Cc/T5_L29_Ca,
         grand_total_vis_by_fte = T5_L34_Cb/T5_L34_Ca,
         ## begin renaming
         phys_fte = T5_L8_Ca,
         phys_vis = T5_L8_Cb,
         phys_virt = T5_L8_Cb2,
         nurses_fte = T5_L11_Ca,
         nurses_vis = T5_L11_Cb,
         nurses_virt = T5_L11_Cb2,
         NP_NPA_CNM_fte = T5_L10a_Ca,
         NP_NPA_CNM_vis = T5_L10a_Cb,
         NP_NPA_CNM_virt = T5_L10a_Cb2,
         total_med_fte = T5_L15_Ca,
         total_med_vis = T5_L15_Cb,
         total_med_virt = T5_L15_Cb2,
         total_med_pat = T5_L15_Cc,
         total_dental_fte = T5_L19_Ca,
         total_dental_vis = T5_L19_Cb,
         total_dental_vis = T5_L19_Cb2,
         total_dental_pat = T5_L19_Cc,
         total_mental_fte = T5_L20_Ca,
         total_mental_vis = T5_L20_Cb,
         total_mental_virt = T5_L20_Cb2,
         total_mental_pat = T5_L20_Cc,
         total_SUD_fte = T5_L21_Ca,
         total_SUD_vis = T5_L21_Cb,
         total_SUD_virt = T5_L21_Cb2,
         total_SUD_pat = T5_L21_Cc,
         total_otherprof_fte = T5_L22_Ca,
         total_otherprof_vis = T5_L22_Cb,
         total_otherprof_virt = T5_L22_Cb2,
         total_otherprof_pat = T5_L22_Cc,
         total_vision_fte = T5_L22d_Ca,
         total_vision_vis = T5_L22d_Cb,
         total_vision_virt = T5_L22d_Cb2,
         total_vision_pat = T5_L22d_Cc,
         total_enabling_fte = T5_L29_Ca,
         total_enabling_vis = T5_L29_Cb,
         total_enabling_virt = T5_L29_Cb2,
         total_enabling_pat = T5_L29_Cc,
         grand_total_fte = T5_L34_Ca,
         grand_total_vis = T5_L34_Cb,
         grand_total_virt = T5_L34_Cb2
         ) %>% 
  select(-T5_L8_Ca:-T5_L34_Cb,-T5_L8_Cb2:-T5_L34_Cb2)
```

Table 5 addendum that was added in 2019 UDS data:

```{r 2019 table 5 addendum}
uds2019info.t5_addendum_rel = uds2019info.t5 %>% 
  select(BHCMISID,
         ReportingYear,
         HealthCenterName,
         mental_phys_personnel = T5_L20a01_Ca1,
         mental_phys_vis = T5_L20a01_Cb,
         mental_phys_virt = T5_L20a01_Cb2,
         mental_phys_pat = T5_L20a01_Cc,
         mental_NP_personnel = T5_L20a02_Ca1,
         mental_NP_vis = T5_L20a02_Cb,
         mental_NP_virt = T5_L20a02_Cb2,
         mental_NP_pat = T5_L20a02_Cc,
         mental_PA_personnel = T5_L20a03_Ca1,
         mental_PA_vis = T5_L20a03_Cb,
         mental_PA_virt = T5_L20a03_Cb2,
         mental_PA_pat = T5_L20a03_Cc,
         mental_CNM_personnel = T5_L20a04_Ca1,
         mental_CNM_vis = T5_L20a04_Cb,
         mental_CNM_virt = T5_L20a04_Cb2,
         mental_CNM_pat = T5_L20a04_Cc,
         SUD_phys_personnel = T5_L21a_Ca1,
         SUD_phys_vis = T5_L21a_Cb,
         SUD_phys_virt = T5_L21a_Cb2,
         SUD_phys_pat = T5_L21a_Cc,
         SUD_NP_personnel = T5_L21b_Ca1,
         SUD_NP_vis = T5_L21b_Cb,
         SUD_NP_virt = T5_L21b_Cb2,
         SUD_NP_pat = T5_L21b_Cc,
         SUD_PA_personnel = T5_L21c_Ca1,
         SUD_PA_vis = T5_L21c_Cb,
         SUD_PA_virt = T5_L21c_Cb2,
         SUD_PA_pat = T5_L21c_Cc,
         SUD_CNM_personnel = T5_L21d_Ca1,
         SUD_CNM_vis = T5_L21d_Cb,
         SUD_CNM_virt = T5_L21d_Cb2,
         SUD_CNM_pat = T5_L21d_Cc,
         SUD_psychiatrist_personnel = T5_L21e_Ca1,
         SUD_psychiatrist_vis = T5_L21e_Cb,
         SUD_psychiatrist_virt = T5_L21e_Cb2,
         SUD_psychiatrist_pat = T5_L21e_Cc,
         SUD_psychologist_personnel = T5_L21f_Ca1,
         SUD_psychologist_vis = T5_L21f_Cb,
         SUD_psychologist_virt = T5_L21f_Cb2,
         SUD_psychologist_pat = T5_L21f_Cc,
         SUD_socialworker_personnel = T5_L21g_Ca1,
         SUD_socialworker_vis = T5_L21g_Cb,
         SUD_socialworker_virt = T5_L21g_Cb2,
         SUD_socialworker_pat = T5_L21g_Cc,
         SUD_othermentalprov_personnel = T5_L21h_Ca1,
         SUD_othermentalprov_vis = T5_L21h_Cb,
         SUD_othermentalprov_virt = T5_L21h_Cb2,
         SUD_othermentalprov_pat = T5_L21h_Cc
         )
```




Now for Table 5a, column B/A calculations and renaming

```{r table 5a}
T5a_rel_numbers = uds2016to2018info.t5.T5A %>% 
  select(#table 5a
         BHCMISID,
         ReportingYear,
         HealthCenterName,
         T5A_L1_Ca,
         T5A_L1_Cb,
         T5A_L2_Ca,
         T5A_L2_Cb,
         T5A_L3_Ca,
         T5A_L3_Cb,
         T5A_L4_Ca,
         T5A_L4_Cb,
         T5A_L5_Ca,
         T5A_L5_Cb,
         T5A_L7_Ca,
         T5A_L7_Cb,
         T5A_L9a_Ca,
         T5A_L9a_Cb,
         T5A_L9b_Ca,
         T5A_L9b_Cb,
         T5A_L10_Ca,
         T5A_L10_Cb,
         T5A_L11_Ca,
         T5A_L11_Cb,
         T5A_L16_Ca,
         T5A_L16_Cb,
         T5A_L17_Ca,
         T5A_L17_Cb,
         T5A_L17a_Ca,
         T5A_L17a_Cb,
         T5A_L20a_Ca,
         T5A_L20a_Cb,
         T5A_L20a1_Ca,
         T5A_L20a1_Cb,
         T5A_L20a2_Ca,
         T5A_L20a2_Cb,
         T5A_L20b_Ca,
         T5A_L20b_Cb,
         T5A_L22a_Ca,
         T5A_L22a_Cb,
         T5A_L22b_Ca,
         T5A_L22b_Cb,
         T5A_L30a1_Ca,
         T5A_L30a1_Cb,
         T5A_L30a2_Ca,
         T5A_L30a2_Cb,
         T5A_L30a3_Ca,
         T5A_L30a3_Cb,
         T5A_L30a4_Ca,
         T5A_L30a4_Cb
         ) %>% 
  bind_rows(uds2014info.T5A_rel,uds2015info.T5A_rel) %>% 
  mutate(ftpt_famphys_mo_by_persons = T5A_L1_Cb/T5A_L1_Ca, #calculations
        ftpt_genprac_mo_by_persons = T5A_L2_Cb/T5A_L2_Ca,
        ftpt_internist_mo_by_persons = T5A_L3_Cb/T5A_L3_Ca,
        ftpt_OBGYN_mo_by_persons = T5A_L4_Cb/T5A_L4_Ca,
        ftpt_ped_mo_by_persons = T5A_L5_Cb/T5A_L5_Ca,
        ftpt_otherspecphys_mo_by_persons = T5A_L7_Cb/T5A_L7_Ca,
        ftpt_NP_mo_by_persons = T5A_L9a_Cb/T5A_L9a_Ca,
        ftpt_PA_mo_by_persons = T5A_L9b_Cb/T5A_L9b_Ca,
        ftpt_CNM_mo_by_persons = T5A_L10_Cb/T5A_L10_Ca,
        ftpt_nurse_mo_by_persons = T5A_L11_Cb/T5A_L11_Ca,
        ftpt_dentist_mo_by_persons = T5A_L16_Cb/T5A_L16_Ca,
        ftpt_dentalhyg_mo_by_persons = T5A_L17_Cb/T5A_L17_Ca,
        ftpt_dentalther_mo_by_persons = T5A_L17a_Cb/T5A_L17a_Ca,
        ftpt_psychiatrist_mo_by_persons = T5A_L20a_Cb/T5A_L20a_Ca,
        ftpt_psychologist_mo_by_persons = T5A_L20a1_Cb/T5A_L20a1_Ca,
        ftpt_socialworker_mo_by_persons = T5A_L20a2_Cb/T5A_L20a2_Ca,
        ftpt_othermentalhealth_mo_by_persons = T5A_L20b_Cb/T5A_L20b_Ca,
        ftpt_opthalmologist_mo_by_persons = T5A_L22a_Cb/T5A_L22a_Ca,
        ftpt_optometrist_mo_by_persons = T5A_L22b_Cb/T5A_L22b_Ca,
        ftpt_CEO_mo_by_persons = T5A_L30a1_Cb/T5A_L30a1_Ca,
        ftpt_CMO_mo_by_persons = T5A_L30a2_Cb/T5A_L30a2_Ca,
        ftpt_CFO_mo_by_persons = T5A_L30a3_Cb/T5A_L30a3_Ca,
        ftpt_CIO_mo_by_persons = T5A_L30a4_Cb/T5A_L30a4_Ca,
        
        ftpt_famphys_yr_by_persons = T5A_L1_Cb/T5A_L1_Ca/12, #YEAR calcs
        ftpt_genprac_yr_by_persons = T5A_L2_Cb/T5A_L2_Ca/12,
        ftpt_internist_yr_by_persons = T5A_L3_Cb/T5A_L3_Ca/12,
        ftpt_OBGYN_yr_by_persons = T5A_L4_Cb/T5A_L4_Ca/12,
        ftpt_ped_yr_by_persons = T5A_L5_Cb/T5A_L5_Ca/12,
        ftpt_otherspecphys_yr_by_persons = T5A_L7_Cb/T5A_L7_Ca/12,
        ftpt_NP_yr_by_persons = T5A_L9a_Cb/T5A_L9a_Ca/12,
        ftpt_PA_yr_by_persons = T5A_L9b_Cb/T5A_L9b_Ca/12,
        ftpt_CNM_yr_by_persons = T5A_L10_Cb/T5A_L10_Ca/12,
        ftpt_nurse_yr_by_persons = T5A_L11_Cb/T5A_L11_Ca/12,
        ftpt_dentist_yr_by_persons = T5A_L16_Cb/T5A_L16_Ca/12,
        ftpt_dentalhyg_yr_by_persons = T5A_L17_Cb/T5A_L17_Ca/12,
        ftpt_dentalther_yr_by_persons = T5A_L17a_Cb/T5A_L17a_Ca/12,
        ftpt_psychiatrist_yr_by_persons = T5A_L20a_Cb/T5A_L20a_Ca/12,
        ftpt_psychologist_yr_by_persons = T5A_L20a1_Cb/T5A_L20a1_Ca/12,
        ftpt_socialworker_yr_by_persons = T5A_L20a2_Cb/T5A_L20a2_Ca/12,
        ftpt_othermentalhealth_yr_by_persons = T5A_L20b_Cb/T5A_L20b_Ca/12,
        ftpt_opthalmologist_yr_by_persons = T5A_L22a_Cb/T5A_L22a_Ca/12,
        ftpt_optometrist_yr_by_persons = T5A_L22b_Cb/T5A_L22b_Ca/12,
        ftpt_CEO_yr_by_persons = T5A_L30a1_Cb/T5A_L30a1_Ca/12,
        ftpt_CMO_yr_by_persons = T5A_L30a2_Cb/T5A_L30a2_Ca/12,
        ftpt_CFO_yr_by_persons = T5A_L30a3_Cb/T5A_L30a3_Ca/12,
        ftpt_CIO_yr_by_persons = T5A_L30a4_Cb/T5A_L30a4_Ca/12,
        
         ## begin renaming
        ftpt_famphys_persons = T5A_L1_Ca,
        ftpt_famphys_mo = T5A_L1_Cb,
        ftpt_genprac_persons = T5A_L2_Ca,
        ftpt_genprac_mo = T5A_L2_Cb,
        ftpt_internist_persons = T5A_L3_Ca,
        ftpt_internist_mo = T5A_L3_Cb,
        ftpt_OBGYN_persons = T5A_L4_Ca,
        ftpt_OBGYN_mo = T5A_L4_Cb,
        ftpt_ped_persons = T5A_L5_Ca,
        ftpt_ped_mo = T5A_L5_Cb,
        ftpt_otherspecphys_persons = T5A_L7_Ca,
        ftpt_otherspecphys_mo = T5A_L7_Cb,
        ftpt_NP_persons = T5A_L9a_Ca,
        ftpt_NP_mo = T5A_L9a_Cb,
        ftpt_PA_persons = T5A_L9b_Ca,
        ftpt_PA_mo = T5A_L9b_Cb,
        ftpt_CNM_persons = T5A_L10_Ca,
        ftpt_CNM_mo = T5A_L10_Cb,
        ftpt_nurse_persons = T5A_L11_Ca,
        ftpt_nurse_mo = T5A_L11_Cb,
        ftpt_dentist_persons = T5A_L16_Ca,
        ftpt_dentist_mo = T5A_L16_Cb,
        ftpt_dentalhyg_persons = T5A_L17_Ca,
        ftpt_dentalhyg_mo = T5A_L17_Cb,
        ftpt_dentalther_persons = T5A_L17a_Ca,
        ftpt_dentalther_mo = T5A_L17a_Cb,
        ftpt_psychiatrist_persons = T5A_L20a_Ca,
        ftpt_psychiatrist_mo = T5A_L20a_Cb,
        ftpt_psychologist_persons = T5A_L20a1_Ca,
        ftpt_psychologist_mo = T5A_L20a1_Cb,
        ftpt_socialworker_persons = T5A_L20a2_Ca,
        ftpt_socialworker_mo = T5A_L20a2_Cb,
        ftpt_othermentalhealth_persons = T5A_L20b_Ca,
        ftpt_othermentalhealth_mo = T5A_L20b_Cb,
        ftpt_opthalmologist_persons = T5A_L22a_Ca,
        ftpt_opthalmologist_mo = T5A_L22a_Cb,
        ftpt_optometrist_persons = T5A_L22b_Ca,
        ftpt_optometrist_mo = T5A_L22b_Cb,
        ftpt_CEO_persons = T5A_L30a1_Ca,
        ftpt_CEO_mo = T5A_L30a1_Cb,
        ftpt_CMO_persons = T5A_L30a2_Ca,
        ftpt_CMO_mo = T5A_L30a2_Cb,
        ftpt_CFO_persons = T5A_L30a3_Ca,
        ftpt_CFO_mo = T5A_L30a3_Cb,
        ftpt_CIO_persons = T5A_L30a4_Ca,
        ftpt_CIO_mo = T5A_L30a4_Cb
         ) %>% 
  rowwise() %>% #calculating average of rows
  mutate(overall_phys_yr_by_persons = mean(c(ftpt_famphys_yr_by_persons,
                                             ftpt_genprac_yr_by_persons,
                                             ftpt_internist_yr_by_persons,
                                             ftpt_OBGYN_yr_by_persons,
                                             ftpt_ped_yr_by_persons,
                                             ftpt_otherspecphys_yr_by_persons), na.rm = T),
         overall_med_yr_by_persons = mean(c(ftpt_famphys_yr_by_persons,
                                            ftpt_genprac_yr_by_persons,
                                            ftpt_internist_yr_by_persons,
                                            ftpt_OBGYN_yr_by_persons, 
                                            ftpt_ped_yr_by_persons, 
                                            ftpt_otherspecphys_yr_by_persons, 
                                            ftpt_NP_yr_by_persons,
                                            ftpt_PA_yr_by_persons,
                                            ftpt_CNM_yr_by_persons, 
                                            ftpt_nurse_yr_by_persons), na.rm = T),
         grand_total_year_by_persons =  mean(c(ftpt_famphys_yr_by_persons,
                                               ftpt_genprac_yr_by_persons, 
                                               ftpt_internist_yr_by_persons,
                                               ftpt_OBGYN_yr_by_persons, 
                                               ftpt_ped_yr_by_persons,
                                               ftpt_otherspecphys_yr_by_persons, 
                                               ftpt_NP_yr_by_persons, 
                                               ftpt_PA_yr_by_persons, 
                                               ftpt_CNM_yr_by_persons, 
                                               ftpt_nurse_yr_by_persons, 
                                               ftpt_dentist_yr_by_persons,
                                               ftpt_dentalhyg_yr_by_persons,
                                               ftpt_dentalther_yr_by_persons,
                                               ftpt_psychiatrist_yr_by_persons,
                                               ftpt_psychologist_yr_by_persons,
                                               ftpt_socialworker_yr_by_persons,
                                               ftpt_othermentalhealth_yr_by_persons,
                                               ftpt_opthalmologist_yr_by_persons,
                                               ftpt_optometrist_yr_by_persons,
                                               ftpt_CEO_yr_by_persons,
                                               ftpt_CMO_yr_by_persons,
                                               ftpt_CFO_yr_by_persons,
                                               ftpt_CIO_yr_by_persons), na.rm = T)
         ) %>% 
  select(-T5A_L1_Ca:-T5A_L30a4_Cb)
```

Add column of shortened health center names:

```{r add shortened HC names}
HC_short = 
  readxl::read_excel(".\\UDS_Name_&_HC_Name.xlsx", sheet = "Sheet1") 

T5_rel_numbers = T5_rel_numbers %>% left_join(HC_short, by = "HealthCenterName")
T5a_rel_numbers = T5a_rel_numbers %>% left_join(HC_short, by = "HealthCenterName")
uds2019info.t5_addendum_rel = uds2019info.t5_addendum_rel %>% left_join(HC_short, by = "HealthCenterName")
```

Clean up data to make clean export:

```{r clean up rows}

#Table 5
is.na(T5_rel_numbers) = T5_rel_numbers == "NaN"
T5_rel_numbers = janitor::remove_empty(T5_rel_numbers, which = c("rows", "cols"), quiet = TRUE)
T5_rel_numbers = T5_rel_numbers %>% arrange(HC_name, ReportingYear) %>% select(HC_name, ReportingYear, everything())

#Table 5a
is.na(T5a_rel_numbers) = T5a_rel_numbers == "NaN"
T5a_rel_numbers = janitor::remove_empty(T5a_rel_numbers, which = c("rows", "cols"), quiet = TRUE)
T5a_rel_numbers = T5a_rel_numbers %>% arrange(HC_name, ReportingYear) %>% select(HC_name, ReportingYear, everything())

#Table 5 addendum (2019 data only)
is.na(uds2019info.t5_addendum_rel) = uds2019info.t5_addendum_rel == "NaN"
uds2019info.t5_addendum_rel = janitor::remove_empty(uds2019info.t5_addendum_rel, which = c("rows", "cols"), quiet = TRUE)
uds2019info.t5_addendum_rel = uds2019info.t5_addendum_rel %>% arrange(HC_name, ReportingYear) %>% select(HC_name, ReportingYear, everything())

```


Export excel sheet with only relevant variables for tables 5 and 5a 2016-2018:

```{r}
# Create a blank workbook
OUT <- createWorkbook()

# Add some sheets to the workbook
addWorksheet(OUT, "Table5")
addWorksheet(OUT, "Table5a")
addWorksheet(OUT, "Table5 Addendum (2019 only)")

# Write the data to the sheets
writeData(OUT, sheet = "Table5", x = T5_rel_numbers)
writeData(OUT, sheet = "Table5a", x = T5a_rel_numbers)
writeData(OUT, sheet = "Table5 Addendum (2019 only)", x = uds2019info.t5_addendum_rel)

# Reorder worksheets
#worksheetOrder(OUT) <- c(3,2,1) # no need to reorder at the moment

# Export the file
saveWorkbook(OUT, "relevant_vars_2014to2019_table5_table5a.xlsx", overwrite = FALSE)

```